Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-09-26 packages/spec-haskell/yellowpaper/Paper.tex
[WIP] still in Payment Execution Environment sub section

%% Import Packages
\usepackage{fvextra}
\usepackage{csquotes}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}

@@

%%% include common formatting
\input{lhsfmt.tex}
%%% for ignoring some code
\long\def\ignore#1{}
%%% for creating a paragraph
\newcommand{\lhsparagraph}[1]{\paragraph{#1}\mbox{}\\}

@@

\subsection{Money Distribution Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

This discrete nature of this money distribution model is schematically depicted in {\ref{fig:discrete-md}}:

@@

Payment primitives are functions that takes a money distribution, shared context, some payment instruction (args) and
timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
associative binary operation and an identity element. See \url{https://ncatlab.org/nlab/show/monoid}.} of money
distribution and shared context as outputs:

@@

\subsection{Payment Execution Environment Models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%% Import Packages
\usepackage{hyperref}
\usepackage{fvextra}
\usepackage{csquotes}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{graphicx}

@@

%%% include common formatting
\input{lhsfmt.tex}
%%% for ignoring some code
\long\def\ignore#1{}
%%% for code
\newminted[code]{haskell}{}
\newminted[spec]{haskell}{}

@@

\subsection{Money Distribution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

This discrete nature of this money distribution model is schematically depicted in \ref{fig:discrete-md}:

@@

Payment primitives are functions that takes a money distribution, shared context, some payment instruction (args) and
timestamp as inputs and incremental updates\footnote{Specifically being monoidal, that is in short a set that has
associative binary operation and an identity element. See https://ncatlab.org/nlab/show/monoid. } of money
distribution and shared context as outputs:

@@

\subsection{Payment Execution Environment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The purpose of a payment execution environment is to perform the actual payment primitives taking into account their
conditions, timing and order.

It is out of scope for this paper to survey in-depth the problem space of the operation semantics of payment execution
environments. Nonetheless, a simplified model and some potential extensions to it is discussed briefly.

\subsubsection{Composing Financial Contracts}

@@

\subsubsection{Simplified Execution Environment Models}

\input{PaymentExecutionEnvironment.lhs.tex}
